Using Decision Trees for optimisation rather than classification XXX BETTER TITLE

### 2008-05-13 papers/aics-2008/paper.tex
Brief outline for Carl to look at.

% $Id$
\documentclass[a4paper,12pt,draft]{article}

@@

\newcommand{\numberOFlogFILES}[0]{%
    93%
}

\newcommand{\numberOFrules}[0]{%
    165%
}

\newcommand{\numberOFlogLINES}[0]{%
    60,721,709%
}

\newcommand{\numberOFlogLINEShuman}[0]{%
    60.72 million%
}

@@

% Pull in the acronyms early, so they can be used throughout the text.
\input{logparser-acronyms.tex}

\title{Parsing Postfix log files}
\author{John Tobin \\ School of Computer Science and Statistics \\
Trinity College \\ Dublin 2 \\ Ireland \\ tobinjt@cs.tcd.ie}
\maketitle

@@

    Parsing Postfix logs is much more difficult than it first appears, but
    it \textit{is\/} possible to achieve a high degree of accuracy in
    understanding the logs, and thus accuracy in reconstructing the actions
    taken by Postfix to generate the logs.  This paper describes the
    creation of a parser, documenting the parsing algorithm, explaining the
    difficulties encountered and the solutions developed, with reference to
    an implementation which stores data gleaned from the logs in an SQL
    database.  The gathered data can then be used to optimise current
    anti-spam measures, provide a baseline to test new anti-spam measures
    against, or to produce statistics showing how effective those measures
    are.

@@

XXX POSSIBLE CONFERENCES\@: AICS'S AI-2008 IN CORK, AND SGAI IN CAMBRIDGE
IN DECEMBER\@.

XXX WEKA FOR DECISION TREE DISPLAY\@.

\newpage
\tableofcontents
\listoffigures
\listoftables

\newpage
\input{logparser-introduction.tex}
\input{logparser-background.tex}
\input{logparser-database-schema.tex}
\input{logparser-parsing-rules.tex}
\input{logparser-parsing-algorithm.tex}
\input{logparser-coverage.tex}
\input{logparser-limitations.tex}
\input{logparser-conclusion.tex}
\input{logparser-other-parsers-review.tex}

\bibliographystyle{logparser-bibliography-style}
\bibliography{logparser-bibliography}
\label{bibliography}

\input{logparser-graphs.tex}

% Redefine the command used to produce the glossary title, because the
% default command produces an unnumbered section whereas I want a numbered
% section.
\renewcommand{\glossarytitle}{\section{Glossary}\label{Glossary}}
\printglossary{}
% Redefine the command a second time to produce acronyms instead of a
% glossary.
\renewcommand{\glossarytitle}{\section{Acronyms}\label{Acronyms}}
\printacronym{}

\input{logparser-glossary.tex}
% logparser-acronyms.tex has been included in the preamble so that the
% commands are available throughout the text.
\end{document}

>>>>

% $Id: logparser.tex 545 2008-05-01 20:00:22Z tobinjt $
\documentclass[twocolumn,a4paper,11pt,draft]{article}

@@

@@

\title{Using Decision Trees for optimisation rather than classification
XXX BETTER TITLE}
\author{John Tobin \& Carl Vogel \\ School of Computer Science and Statistics \\
Trinity College \\ Dublin 2 \\ Ireland \\ tobinjt@cs.tcd.ie \&
vogel@cs.tcd.ie }
\maketitle

@@

    Classification performed by evaluating user-defined sequences of tests
    can be optimised by applying a Decision Tree algorithm to data gathered
    from running the tests, providing the user with a more efficient or
    more accurate sequence of tests.  This usage of Decision Trees is
    illustrated by optimising Postfix~\cite{postfix} anti-spam
    restrictions~\cite{smtpd_access_readme}, a task complicated by the
    division of the tests into groups, restricting the Decision Tree
    algorithm to examining subsets of attributes at a time.

@@

\section{Introduction}

Motivation, background on Postfix restrictions (appendix maybe?)

\section{Algorithm}

Standard CART Decision Tree with modifications:

\begin{itemize}

    \item groups of attributes to examine

    \item result already known --- non-rejections will be weeded out into
        the false branches, eventually ending up in the bottom-left-most
        leaf node.

    \item scoring functions

\end{itemize}

\section{Results}

\begin{itemize}

    \item duplicate rows collapsed; histograms of distribution

    \item optimised ordering --- primary component analysis

    \item image

    \item different trees from different scoring functions

\end{itemize}

\section{Conclusion}

Useful for optimisation and visualisation.

\appendix

\bibliographystyle{../common/bibliography-style}
\bibliography{../common/bibliography}
\label{bibliography}

\end{document}
